### 2025-09-08 short/sections/selected-papers.tex
Update selected-papers.tex

\item{González-Bustamante, B. (2025, {\itshape forthcoming}). Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval. {\itshape Public Opinion Quarterly}. SocArXiv: \href{https://doi.org/10.31235/osf.io/37ruy_v1}{\textcolor{blue}{10.31235/osf.io/37ruy\_v1}}.}\vspace{1mm}

\item{Kantorowicz, J., \& González-Bustamante, B. (2025). Changing Meaning of the Rule of Law. {\itshape Artificial Intelligence and Law}. OnlineFirst. DOI: \href{https://doi.org/10.1007/s10506-025-09468-4}{\textcolor{blue}{https://doi.org/10.1007/s10506-025-09468-4}}. OSF: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}

\item{González-Bustamante, B. (2025). Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets. {\itshape Social Science Computer Review}. OnlineFirst. DOI: \href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper / Writing sample}.}\vspace{1mm}

>>>>

\item{González-Bustamante, B. (2025, {\itshape forthcoming}). Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval. {\itshape Public Opinion Quarterly}. SocArXiv: \href{https://doi.org/10.31235/osf.io/37ruy_v2}{\textcolor{blue}{10.31235/osf.io/37ruy\_v2}}.}\vspace{1mm}

\item{Kantorowicz, J., \& González-Bustamante, B. (2025). Changing Meaning of the Rule of Law. {\itshape Artificial Intelligence and Law}. OnlineFirst. DOI: \href{https://doi.org/10.1007/s10506-025-09468-4}{\textcolor{blue}{10.1007/s10506-025-09468-4}}. OSF: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}

\item{González-Bustamante, B. (2025). Machine Learning and Political Events: Application of a Semi-supervised Approach to Produce a Dataset on Presidential Cabinets. {\itshape Social Science Computer Review}. OnlineFirst. DOI: \href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper / Writing sample}.}\vspace{1mm}
